### 2017-11-30 manuscript.rmd
removed unnecessary columns from main_characters, corrected for column number shifts in manuscripts, removed unnecesary variable declarations

vrange = cdata$Vertical.range
names(vrange) = rownames(cdata)

@@

depth_median = dpruned_data$Depth.Median
names(depth_median) = rownames(dpruned_data)

depth_mean = dpruned_data$Depth.Mean
names(depth_mean) = rownames(dpruned_data)

depth_min = dpruned_data$Depth.Min
names(depth_min) = rownames(dpruned_data)

depth_max = dpruned_data$Depth.Max
names(depth_max) = rownames(dpruned_data)

depth_sd = dpruned_data$Depth.StdDev
names(depth_sd) = rownames(dpruned_data)

depth_range = depth_max - depth_min

abundance = dpruned_data$Depth.Count
names(abundance) = rownames(dpruned_data)

@@

```{r ggtree_bin_heatmap, echo=F, message=F, warning=F, include=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=2.2)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(1,2,5:8,12)]
rownames(f_cdata) = rownames(cdata)
f_cdata = f_cdata[,c(4,7,1,3,6,2,5)]
f_cdata[match(tree$tip.label,rownames(f_cdata)),]
# pdf("figures_for_AI/overview_ggheatmap_chars.pdf")
# gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1)
# dev.off()
```

>>>>

@@

depth_median = dpruned_data$Depth.Median
names(depth_median) = rownames(dpruned_data)
```

@@

```{r ggtree_bin_heatmap, echo=F, message=F, warning=F, include=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=2.2)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(1,2,5:9)]
rownames(f_cdata) = rownames(cdata)
f_cdata = f_cdata[,c(4,7,1,3,6,2,5)]
f_cdata[match(tree$tip.label,rownames(f_cdata)),]
# pdf("figures_for_AI/overview_ggheatmap_chars.pdf")
# gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1)
# dev.off()
```
